SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-07 docs/questioning.tex
minor changes

\noindent
All the aforementioned requirements are considered critical
when building security mechanisms that protect
applications~\cite{A01,A00,SPWS13}. Based on this analysis
we can identify the advantages and disadvantages of the
various mechanisms and enumerate some of their common
characteristics. We can also draw useful conclusions
about the various categories and see how they compare
to each other.

@@

Defenses based on training include some mechanisms that can be easily
circumvented. For example, {\sc didafit} records all database
transactions without tagging each transaction with the
corresponding call-site. In this case a false negative result
is prominent. For instance, consider an application that will send the
password for a forgetful user via email by executing the following
query: \bgroup \lstset{language=SQL}
\begin{small}
\begin{lstlisting}
SELECT password from userdata WHERE id = 'Alice'
\end{lstlisting}
\end{small}
\egroup
\noindent
This same application could allow users to lock their terminal,
but allow the unlocking either with the user's password or with
the administrator password (the 4.3 {\sc bsd} {\em lock} command
behaved in this peculiar way).
The corresponding query to verify the password on the locked
workstation would be as follows:
\bgroup
\lstset{language=SQL}
\begin{small}
\begin{lstlisting}
SELECT password from userdata WHERE id = 'Alice' OR
id = 'admin'
\end{lstlisting}
\end{small}
\egroup
\noindent
In this case {\sc didafit}, could be easily escaped
since a malicious user, could obtain the administrator's password
by email by entering on the password retrieval form
as his user identifier the following:
\bgroup
\lstset{language=SQL}
\begin{small}
\begin{lstlisting}
nosuchuser' OR id = 'admin
\end{lstlisting}
\end{small}
\egroup
\noindent
%% PL I do not understand what is specific to training here; most
%% classic SQL injection attacks work in this way.
However, mechanisms that create signatures that involve
elements not only associated with the code statements
(i.e. {\sc amnesia} and {\sc sd}river)
could detect such attacks. Specifically,
{\sc sd}river associates a complete stack trace with the
root of an {\sc sql} statement, thus it can correlate
queries with their call sites and detect attacks
like the aforementioned one.
Furthermore, training tools that detect
{\sc xss} attacks based on JavaScript injection
would fail to detect a return-to-JavaScript
attack~\ref{APKLM10}.
%% PL Like the return-to-lib attack?

>>>>

\noindent
All the aforementioned requirements are considered critical
when building security mechanisms that protect
applications~\cite{A01,A00,SPWS13,nature2014}.
Based on this analysis we can identify the advantages
and disadvantages of the
various mechanisms and enumerate some of their common
characteristics. We can also draw useful conclusions
about the various categories and see how they compare
to each other.

@@

Defenses based on training include some mechanisms that can be easily
circumvented. For example, {\sc didafit} records all database
transactions without tagging each transaction with the
corresponding call-site. In this case a false negative result
is prominent. For instance, consider an application that will send the
password for a forgetful user via email by executing the following
query: \bgroup \lstset{language=SQL}
\begin{small}
\begin{lstlisting}
SELECT password from userdata WHERE id = 'Alice'
\end{lstlisting}
\end{small}
\egroup
\noindent
This same application could allow users to lock their terminal,
but allow the unlocking either with the user's password or with
the administrator password (the 4.3 {\sc bsd} {\em lock} command
behaved in this peculiar way).
The corresponding query to verify the password on the locked
workstation would be as follows:
\bgroup
\lstset{language=SQL}
\begin{small}
\begin{lstlisting}
SELECT password from userdata WHERE id = 'Alice' OR
id = 'admin'
\end{lstlisting}
\end{small}
\egroup
\noindent
In this case {\sc didafit}, could be easily escaped
since a malicious user, could obtain the administrator's password
by email by entering on the password retrieval form
as his user identifier the following:
\bgroup
\lstset{language=SQL}
\begin{small}
\begin{lstlisting}
nosuchuser' OR id = 'admin
\end{lstlisting}
\end{small}
\egroup
\noindent
%% PL I do not understand what is specific to training here; most
%% classic SQL injection attacks work in this way.
However, mechanisms that create signatures that involve
elements not only associated with the code statements
(i.e. {\sc amnesia} and {\sc sd}river)
could detect such attacks. Specifically,
{\sc sd}river associates a complete stack trace with the
root of an {\sc sql} statement, thus it can correlate
queries with their call sites and detect attacks
like the aforementioned one.
Furthermore, training tools that detect
{\sc xss} attacks based on JavaScript injection
would fail to detect a return-to-JavaScript
attack~\cite{APKLM10}.
%% PL Like the return-to-lib attack?
